Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-10-23 latex/paper.tex
按照郭志新的意见修改introduction

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-10-23 17:41:29
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

With the development1 of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials. The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size. For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}. Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}. Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}. However, materials prepared in the practical application is often multilayer structure to a few nanometers. Previous studies have focused on the weak Van der Waals interaction (vdW), and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicon material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicon, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.

Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon. The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.

At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}. Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications. However, the study on the properties of multilayer silicon thermal transport is still very rare, To this end, based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-10-23 21:19:00
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

Many theorical experiment result has shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them potential in the application of thermalelectric field where the thermalelectric figure of merit $ZT=\frac{S^2 \sigma T}{\kappa}$ could be optimized by the reduced thermal condutvitiy. For example
the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicon nanowires.At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}. Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications. However, the study on the properties of multilayer silicon thermal transport is still very rare.

The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicon material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicon, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials. The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.

Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases. For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}. Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}. Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}. In the case of silicon, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}. And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction. This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.

In this work we use multilayer silicon as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon. The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future. Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.
